Introduction to\\ Swedish Civil Contingencies Agency (MSB) methodological support for introducing \ac{isms}.

### 2019-03-15 msbframework/msbintro/msbintro.tex
Updated slides, changed order

\begin{frame}{Analyse Informational Assets}
  \begin{block}
    Informational assets are the organisations information and its resources
    that deals with information. For example to receive, store, process, show or
    communicate it~\cite{msb_metodstod}.
  \end{block}
\end{frame}

@@

@@

\subsection{Risk analysis}
\begin{frame}{Risk analysis}
  \begin{itemize}
    \item Identifies the information security risks.
    \item Can be performed over generally over the organisation, or on a
      specific object.
    \item The identified risks are then assessed based on probability and
      consequence.
  \end{itemize}
\end{frame}

\begin{frame}{When should the Risk Analysis be performed?}
  \begin{itemize}
    \item Not necessary to perform the risk analysis after the business
      intelligence and organisational analysis.
    \item If it is performed after, then the results from these can be used in
      the risk analysis.
    \item Otherwise, it is possible to rely on the existing knowledge of the
      organisation.
  \end{itemize}
\end{frame}

>>>>

\begin{frame}{Analyse Informational Assets}
  \begin{block}{Informational Assets}
    Informational assets are the organisations information and its resources
    that deals with information. For example to receive, store, process, show or
    communicate it~\cite{msb_metodstod}.
  \end{block}
\end{frame}

@@

\begin{frame}{Documenting the informational assets}
  When documenting the informational assets, ensure that at least the following
  is documented:
  \begin{itemize}
    \item Name
    \item Description
    \item Type of information, for example personal data.
    \item Critical?
    \item Owner and contact information
  \end{itemize}
\end{frame}

\subsection{Risk analysis}
\begin{frame}{Risk analysis}
  \begin{itemize}
    \item Identifies the information security risks.
    \item Can be performed over generally over the organisation, or on a
      specific object.
    \item The identified risks are then assessed based on probability and
      consequence.
  \end{itemize}
  \begin{block}{What to acheive with a risk analysis}
    \begin{itemize}
      \item What can happen?
      \item How probable is it?
      \item What is the consequences?
    \end{itemize}
    Note that the result of the risk analysis shouldn't be seen as the absolute
    truth.
  \end{block}
\end{frame}

\begin{frame}{When should the Risk Analysis be performed?}
  \begin{itemize}
    \item Not necessary to perform the risk analysis after analysing the
      organisation or external and legal requirements.
    \item If it is performed after, then the results from these can be used in
      the risk analysis.
    \item Otherwise, it is possible to rely on the existing knowledge of the
      organisation.
  \end{itemize}
\end{frame}
\begin{frame}{When should the Risk Analysis be performed?}
  Examples of when it can be suitable to perform a risk analysis.
  \begin{itemize}
    \item Procuring new services?
    \item Outsouring
    \item Organisational changes
  \end{itemize}
\end{frame}

@@

%=======================================================================%
